Bridging [TBD]

### 2014-03-19 paper/draft.tex
Updated intro.

Cloud computing platform are a solid reality nowadays. Modern cloud platforms are able to provide elastic use of resources, optimizing their allocation in order to meet the user needings. However, currently deployed cloud platforms present still several limitations.

First, it is still difficult to deliver cloud applications which are able to transparently leverage over several platform resources. The concept of SuperCloud~\cite{art:blan, xclo:blank} addresses this kind of problems. Multi-platform coordination primarily for different standard and several format lock-in. Unfortunately, those lock-in are not only due to market strategical decisions but they also reflects the virtualization technology heterogeneity. For example, each cloud provider could use a different storage system or a different format to store VMs images. Different hypervisors have nowadays a low degree of compatibility between them and this generally prevents leveraging on some popular features like `` VM live migration'' between different platform. Moreover, this incompatibility could also be enlarged if we consider that several platforms adopts one or more different virtualization techniques. In addition, this situation induce a tight dependency between the customer and the cloud provider and hardens the possibility to guarantee the availability of service in presence of a certain provider or to put in place some geographical optimization due to cost or traffic origin. The result was that some data server failures in the past has been catastrophic, causing a prolonged outage of service for a plenty of applications.. In the remaining part of the work, we will refer to those issues as ``horizontal'' requirements, that shows straightforwardly their multi-platform nature.

>>>>

\noindent Cloud computing is now a solid reality. Modern cloud platforms are able to provide elastic use of resources, optimizing their allocation to meet user needs. However, currently deployed cloud infrastructures present several limitations.

First, it is still difficult to deploy cloud applications able to transparently leverage resources of several heterogeneous platforms. The concept of super-cloud~\cite{art:blan, xclo:blank} tries notably to overcome such issues. Multi-platform coordination is hard, primarily due to lock-in to different standards such as VM formats. Unfortunately, such lock-in is not only due to market strategic decisions, but also reflects heterogeneity of virtualization technologies. For example, each cloud provider may use different storage systems or different formats to store VMs images. Different hypervisors have nowadays a low degree of compatibility between them. This generally prevents leveraging some popular features like VM live migration between different platforms. Incompatibility is even greater if we consider that each platform may adopt several types of virtualization techniques. This situation induces a tight dependency between the customer and the cloud provider. It may prevent guaranteeing service availability by relying on alternative providers, or to set up geographical optimizations due to cost or origin of traffic. This has resulted in some dramatic data server failures in recent years, causing prolonged outage of service for many applications. In what follows, we refer to this class of challenges as \textit{horizontal}, to highlight their multi-platform nature.
